Measuring matter effects in Neutron star - Black hole binaries with Advanced LIGO

### 2016-04-13 Paper/paper.tex
updated all mult obs figs
some new population figures

% \begin{figure}
% \includegraphics[width=1.\columnwidth]{plots/FillBetweenRelErrorBarsLambda_vs_NShifted_AllLambda.pdf}
% \caption{HELLO
% \label{fig:TT_Lambda_vs_N_L500_2000_CI90_0_AllInOne}
% \end{figure}

@@

\includegraphics[width=1\columnwidth]{plots/RelErrorLambdaMedian_vs_N.pdf}
\includegraphics[width=1\columnwidth]{plots/LambdaCIWidths_vs_N.pdf}
\caption{{\it Left}: In the main panel is shown the width of the measured $90\%$ 
 {\it Right}: This figure shows the fractional difference between the median

@@

@@

\includegraphics[width=\columnwidth]{plots/PowerLawCoefficient_LambdaErrorvsN_vs_Lambda.pdf}

@@

\includegraphics[width=\columnwidth]{plots/LambdalErrorBars_vs_Lambda_N79_Log.pdf}
\includegraphics[width=\columnwidth]{plots/PowerLawCoefficient_LambdaErrorvsLambda_vs_N.pdf}

>>>>

@@

\includegraphics[trim=20 0 0 0, width=1.05\columnwidth]{plots/LambdaMedian_vs_N_AllPopulation}
\caption{This figure shows the fractional difference between the median

@@

\label{fig:TT_Lambda_vs_N_L500_2000_CI90_0_AllInOne}
% \begin{figure*}
% \includegraphics[width=1.03\columnwidth]{plots/RelErrorLambdaMedian_vs_N.pdf}
% \includegraphics[width=1.03\columnwidth]{plots/LambdaCIWidths_vs_N.pdf}
% \caption{{\it Left}: In the main panel is shown the width of the measured $90\%$ 
% confidence interval for $\lambdans$, normalized by its true value,
%  as a function of the number of events observed $N$. In the inset, we
%  show the same measurement uncertainty, but not normalized, and on a 
%  logarithmic axis for $N$ as well.
%  From both the inset and the main plot, we find that for the first $3-4$ events
%  our measurement is prior limited. As $N$ increases, the uncertainty falls 
%  roughly as $1/\sqrt{N}$ with intermittent loud signals causing more rapid 
%  (than $1/\sqrt{N}$) narrowing of the confidence interval.
%  {\it Right}: This figure shows the fractional difference between the median
%  recovered value from the posterior probability distribution for $\lambdans$
%  as a function of $N$. Different curves correspond to different injected values
%  of $\lambdans$, and are shaded from light to dark in direct proportion. 
%  The horizontal dashed brown line marks $10\%$ deviation of the median from the 
%  true value.
% We find that within $\approx 10$ detections, the median measured value for
% $\lambdans$ would estimate the true value for the star with the remarkable 
% accuracy of $10\%$.
% \label{fig:TT_LambdaError_vs_N_L500_2000_CI90_0}
% \end{figure*}
%LambdaCIWidths_vs_N_AllPopulations_Log_L
\includegraphics[width=.9\columnwidth]{plots/LambdaCIWidths_vs_N_AllPopulations_Log_L2000.pdf}
\includegraphics[width=.9\columnwidth]{plots/LambdaCIWidths_vs_N_AllPopulations_Log_L1500.pdf}\\
\includegraphics[width=.67\columnwidth]{plots/LambdaCIWidths_vs_N_AllPopulations_Log_L1000.pdf}
\includegraphics[width=.67\columnwidth]{plots/LambdaCIWidths_vs_N_AllPopulations_Log_L800.pdf}
\includegraphics[width=.67\columnwidth]{plots/LambdaCIWidths_vs_N_AllPopulations_Log_L500.pdf}
\caption{ In the main panel is shown the width of the measured $90\%$ 

@@

\includegraphics[width=1.05\columnwidth]{plots/PowerLawCoefficient_LambdaErrorvsN_vs_N.pdf}

@@

% \includegraphics[width=1.03\columnwidth]{plots/LambdaRelErrorBars_vs_Lambda_AllPopulations_N80_Log.pdf}
\includegraphics[width=\columnwidth]{plots/PowerLawCoefficient_LambdaErrorvsLambda_vs_N_AllPopulations.pdf}
